Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-11 podc16/paper2.tex
dependency-set algo - first part

@@

@@

>>>>

An example of implementation of such an algorithm is depicted by the pseudocode of \Cref{fig:deps-set-algo}. The idea is to let every process broadcast $c$ to all the processes in the system, in order to announce $c$. Then whenever a process $p$ receives $c$, it replies to the sender with the set $\mathcal{D}$ of commands that $p$ has observed so far, and such that $c$ and any command in $\mathcal{D}$ are \textit{non-commutative}. Afterwards, the process announcing $c$ collects the sets $\mathcal{D}$ for $c$ from a quorum of $\mathcal{Q}$ processes, and it locally suggests the union of those sets as final dependency-set for $c$.

The provided implementation satisfies the two properties of a dependency-set algorithm for the following reasons. Since any command in a dependency-set that is suggested by a process must be in the set $cmds_q$ of the commands received by some process $q$, and a process receives a command if and only if there exists some process that previously announced the command, then it follows that any command in any suggested dependency-set has been previously announced.

\begin{figure*}
\centering
\subfigure[$\texttt{init}_p$ and $\texttt{announce}_p$ implementations.]{
\noindent\fbox{%
	\begin{varwidth}{\dimexpr\linewidth-2\fboxsep-2\fboxrule\relax}

		\begin{algorithmic}[1]
			{\small
			\START[\texttt{init$_p$}]{{\bf upon}}{$()$} \label{alg:init}
			\State $cmds_p\gets\emptyset$ \label{alg:init-cmds}
			\State $\forall c,$ $deps_p[c]\gets \emptyset$ \label{alg:init-deps}
			\State $\forall c,$ $heard_p[c]\gets \emptyset$ \label{alg:init-heard}
			\State $\forall c,$ $suggested_p[c]\gets false$ \label{alg:init-suggested}
			\END
			\Statex
			\START[\texttt{announce$_p$}]{{\bf upon}}{$(c)$} \label{alg:announce}
			\State $cmds_p\gets cmds_p\cup\{c\}$ \label{alg:add-command}
			\State $\forall q\in P$ {\bf send} $\langle \texttt{cmd}$ $|$ $c \rangle$ {\bf to} $q$\label{alg:send-new-cmd}
			\END
			}
		\end{algorithmic}
	\end{varwidth}%
}
\label{fig:deps-set-algo1}
}
\hspace*{0.3in}\subfigure[receive of \texttt{cmd} and \texttt{deps} messages, and suggestion of dependencies for a command on process $p$.]{
\noindent\fbox{%
	\begin{varwidth}{\dimexpr\linewidth-2\fboxsep-2\fboxrule\relax}

		\begin{algorithmic}[1]
			{\small
			\START[$\langle \texttt{cmd}$ $|$ $c \rangle$]{{\bf upon receive}}{ {\bf from} $q$} \label{alg:receive-new-cmd}
			\State $\mathcal{D} \gets \{ d : d \in cmds_p \land d\neq c \land d \asymp c \}$
			\State $cmds_p\gets cmds_p\cup\{c\}$
			\State {\bf send} $\langle \texttt{deps}$ $|$ $c,\mathcal{D} \rangle$ {\bf to} $q$\label{alg:send-deps}
			\END
			\Statex
			\START[$\langle \texttt{deps}$ $|$ $c,\mathcal{D} \rangle$]{{\bf upon receive}}{ {\bf from} $q$} \label{alg:receive-deps}
			\State $deps_p[c]\gets deps_p[c]\cup \mathcal{D}$
			\State $heard_p[c]\gets heard_p[c]\cup \{q\}$
			\END
			\Statex
			\START[]{{\bf upon}}{$\exists c$ $:$ $ | heard_p[c] | \geq \mathcal{Q}$ $\land$ $suggested_p[c]=false$} \label{alg:receive-deps}
			\State $suggested_p[c]\gets true$
			\State {\bf call} $\texttt{suggest}_p(c,deps_p[c])$
			\END
			}
		\end{algorithmic}
	\end{varwidth}%
}
\label{fig:deps-set-algo2}
}
\caption{Example of dependency-set algorithm implementation.}
\label{fig:deps-set-algo}
\end{figure*}

@@

\todo{Write a suggestion on about GC of dependencies. Remove any command c such that a committed command depends on c. Also us the GC of the map-agreement component.}

@@

\todo{Cite Generalized Paxos as an example for bounding the data structures.}
